---
title: "descriptions"
format: html
editor: visual
---

```{r}
library(rvest)
library(tidyverse)
```

> **Goal:** Scrape information from <https://www.cheese.com> to obtain a dataset of characteristics about different cheeses, and gain deeper insight into your coding process. 🪤

# Part 1

**Part 1:** Locate and examine the `robots.txt` file for this website. Summarize what you learn from it.

The `robots.txt` file is good news for us. The User-agent is \*, meaning that anyone is allowed to scrape. This gives us the green light to scrape the data from this website. There are also no restrictions: no crawl-delay, no visit-time, no request-rate, and no disallow sections. The only other thing present is a Sitemap link, which provides the location of the XML sitemap which provides details of the different website pages.

# Part 2

**Part 2:** Learn about the `html_attr()` function from `rvest`. Describe how this function works with a small example.

The `html_attr()`function extracts a single HTML attribute from a webpage. The first argument, `x`, is a document from the `read_html` function (i.e. read_html("burgers.com")). The second argument, `name`, is the name of the attribute to retrieve. For example, "a" will specify links on the page. The last (optional) argument, `default`, is what is used for when the specified attribute does not exist in every element. It usually needs to be used with the `html_elements()` since `html_attr()` does not expect to receive the entire HTML document as the first argument.

An example of this function would be the following:

```{r}
cheesepage <- read_html("https://www.cheese.com/")

link_urls <- cheesepage %>%
  html_elements("a") %>%
  html_attr("href")

link_urls[1:10]
```
#Part 5

**Part 5:** When you go to a particular cheese's page (like [gouda](https://www.cheese.com/gouda/)), you'll see more detailed information about the cheese. For [**just 10**]{.underline} of the cheeses in the database, obtain the following detailed information:

-   milk information
-   country of origin
-   family
-   type
-   flavour

(Just 10 to avoid overtaxing the website! Continue adding a 1 second pause (use Sys.sleep(1)) between page queries.)

Ok so we need to write a function (or two) to get everything for one cheese then iterate that function to get it for 10 cheeses, put everything in a df/tibble i think, 1 row per cheese?

testing just code

```{r}
page <- read_html("https://www.cheese.com/gouda/")
```

```{r}
page %>%
  html_elements(".summary_taste p , .summary_milk p , .summary_moisture_and_type p , .summary_family p , .summary_country p") %>%
  html_text(trim = TRUE) %>%
  tibble() 
```

```{r}
#get the url to scrape from
base_url <- "https://www.cheese.com/"

get_page <- function(cheese) {
  
  if (!is.vector(cheese) | !is.atomic(cheese)) {
    stop("The input for `cheese` must be a vector or a character string.")
  }

  page_url <- paste0(base_url, cheese, "/")
  return(page_url)
}
```

function writing

```{r}
grab_text <- function(page, css){
  
  page %>%
    html_elements(css) %>%
    html_text(trim = TRUE)
}

scrape <- function(link, delay = 1) {
  Sys.sleep(delay)
  
  page <- read_html(link)
  
  
}
```

testing
```{r}
get_cheese_attribute <- function(webpage, selector_class) {
  webpage %>%
    html_elements(paste0(".", selector_class, " p")) %>%
    html_text(trim = TRUE) %>%
    # Return first element or NA if empty
    (\(x) if(length(x) > 0) x[1] else NA_character_)()
}
```


```{r}
base_url <- "https://www.cheese.com/"

get_cheese_data <- function(cheese) {
  # if (!is.vector(cheese_vec)) {
  #   stop("The input for `cheese` must be a vector of cheese names!")
  # }
  
  page_url <-  paste0(base_url, cheese, "/")
  Sys.sleep(1)
  
  # Read the HTML content from the webpage
  webpage <- read_html(page_url)
  
  # Pull cheese taste 
  cheese_taste <- webpage %>%
    html_elements(".summary_taste p") %>%
    html_text(trim = TRUE)
  
  # Pull cheese milk summ
  cheese_milk <- webpage %>%
    html_elements(".summary_milk p") %>%
    html_text(trim = TRUE)
  
  # Pull cheese moisture type summ
  cheese_type <- webpage %>%
    html_elements(".summary_moisture_and_type p ") %>%
    html_text(trim = TRUE)
  
  # Pull cheese family summ
  cheese_family <- webpage %>%
    html_elements(".summary_family p ") %>%
    html_text(trim = TRUE)
  
  # Pull cheese country
  cheese_country <- webpage %>%
    html_elements(".summary_country p ") %>%
    html_text(trim = TRUE)
  
  
  # Return the dataframe with everything (used chatgpt to remind me how to split strings)
  return(data.frame(
    Name = cheese,
    Taste = sub(".*:\\s*", "", cheese_taste),
    Milk = cheese_milk,
    Type = sub(".*:\\s*", "", cheese_type),
    Family = sub(".*:\\s*", "", cheese_family),
    Country = sub(".*:\\s*", "", cheese_country)
  ))
}
```

```{r}
# Apply the scrape_page function to all pages of cheese.com (doesnt work had to revise function)
all_cheese_data <- lapply(c("acapella", "accasciato", "ackawi", "acorn", "adelost", "adl-brick-cheese", "adl-mild-cheddar", "admiral-collingwood", "zamorano", "ziller"), get_cheese_data)
```

## copy everything below this for number 5

```{r}
# Function to scrape a single cheese
scrape_cheese <- function(cheese, base_url, delay = 1) {
  
  #set up page url to grab 
  page_url <- paste0(base_url, cheese, "/")
  
  #include sys delay so we don't overload the website
  Sys.sleep(delay)
  
  # This is a cool new thing that Claude included in its revision. tryCatch handles errors pretty nicely
  # It gives a structure to any errors that occurs and still gives a blank df as output
  tryCatch({
    # read the webpage url
    webpage <- read_html(page_url)
    
    # helper function to grab from each css instead of copy pasting 5 blocks for each css
    get_cheese_attribute <- function(css) {
      result <- webpage %>%
        html_elements(paste0(".", css, " p")) %>%
        html_text(trim = TRUE)
      
      # return empty string if nothing is found
      if(length(result) == 0) return("")
      result[1]
    }
    
    # grab and store every desired attribute
    cheese_taste <- get_cheese_attribute("summary_taste")
    cheese_milk <- get_cheese_attribute("summary_milk")
    cheese_type <- get_cheese_attribute("summary_moisture_and_type")
    cheese_family <- get_cheese_attribute("summary_family")
    cheese_country <- get_cheese_attribute("summary_country")
    
    # return the dataframe with everything, with some additional string cutting
    data.frame(
      Name = cheese,
      Taste = sub(".*:\\s*", "", cheese_taste),
      Milk = cheese_milk,
      Type = sub(".*:\\s*", "", cheese_type),
      Family = sub(".*:\\s*", "", cheese_family),
      Country = sub(".*:\\s*", "", cheese_country)
    )
    #now, tryCatch kicks in, just in case there is any error
  }, error = function(error_message) {
    
    #give warning message
    warning(paste("Failed to scrape cheese:", cheese, "-", error_message$message))
    
    # return empty df
    data.frame(
      Name = cheese,
      Taste = NA_character_,
      Milk = NA_character_,
      Type = NA_character_,
      Family = NA_character_,
      Country = NA_character_
    )
  })
}
# claude helped with editing original functions
```

```{r}
# apply single cheese function to one for multiple cheeses
scrape_cheeses <- function(cheese_vec, base_url, delay = 1) {
  
  # check if vector and is 10 or less long
  if (!is.vector(cheese_vec) | length(cheese_vec) > 10) {
    stop("The input for `cheese_vec` must be a vector of cheese names of length 10 or lower!")
  }
  
  # go through each cheese and apply the function
  #used claude to remember the syntax for map, forgot you had to do .x
  map_dfr(cheese_vec, ~{
    scrape_cheese(.x, base_url, delay)
  })
  
}
```

```{r}
# base URL
base_url <- "https://www.cheese.com/" 

cheese_list <- c("brie", "gouda", "feta", "mozzarella", "camembert", "stilton", "ricotta", "limburger", "swag", "american-cheese")
cheese_output <- scrape_cheeses(cheese_list, base_url)
cheese_output
```

# Part 6

**Part 6:** Evaluate the code that you wrote in terms of **efficiency**. To
what extent do your function(s) adhere to the **principles for writing good functions**?
To what extent are your **functions efficient**? To what extent is your 
**iteration of these functions efficient**? 

## talk about part 5 functions here

I think the functions are well-commented and explain what they are doing. The body is relatively easy to read. The parameter names are also informative at a baseline level. The output is generally predictable, with a tryCatch() and if statement to give errors in case something goes wrong. However, I do not think that these will catch every type of error or misused parameter that could be present in the function. The functions are also self contained. 

However, I think the efficiency could leave a little more to be desired. There is probably a way to just use one function to scrape multiple cheeses, instead of making one function to do one cheese and another to iterate through multiple cheeses. The substring method I used (sub()) might be able to be made into a helper function since it is repeated in a couple of places. The iteration I do have present seems efficient since it directly applies the existing function to a vector and outputs a data frame.