---
title: "descriptions"
format: html
editor: visual
---

```{r}
library(rvest)
library(tidyverse)
```


> **Goal:** Scrape information from <https://www.cheese.com> to obtain a dataset
> of characteristics about different cheeses, and gain deeper insight into your
> coding process. 🪤

**Part 1:** Locate and examine the `robots.txt` file for this website. Summarize
what you learn from it.

The `robots.txt` file is good news for us. The User-agent is *, meaning that anyone is allowed to scrape. This gives us the green light to scrape the data from this website. There are also no restrictions: no crawl-delay, no visit-time, no request-rate, and no disallow sections. The only other thing present is a Sitemap link, which provides the location of the XML sitemap which provides details of the different website pages.

**Part 2:** Learn about the `html_attr()` function from `rvest`. Describe how
this function works with a small example.

The `html_attr()`function extracts a single HTML attribute from a webpage. The first argument, `x`, is a document from the `read_html` function (i.e. read_html("burgers.com")). The second argument, `name`, is the name of the attribute to retrieve. For example, "a" will specify links on the page. The last (optional) argument, `default`, is what is used for when the specified attribute does not exist in every element. It usually needs to be used with the `html_elements()` since `html_attr()` does not expect to receive the entire HTML document as the first argument. 

An example of this function would be the following:

```{r}
cheesepage <- read_html("https://www.cheese.com/")

link_urls <- cheesepage %>%
  html_elements("a") %>%
  html_attr("href")

link_urls[1:10]
```

**Part 5:** When you go to a particular cheese's page (like 
[gouda](https://www.cheese.com/gouda/)), you'll see more detailed information
about the cheese. For [**just 10**]{.underline} of the cheeses in the database,
obtain the following detailed information:

-   milk information
-   country of origin
-   family
-   type
-   flavour

(Just 10 to avoid overtaxing the website! Continue adding a 1 second pause (use Sys.sleep(1)) between page queries.)

Ok so we need to write a function (or two) to get everything for one cheese then iterate that function to get it for 10 cheeses, put everything in a df/tibble i think, 1 row per cheese?


test just code

```{r}
page <- read_html("https://www.cheese.com/gouda/")
```

```{r}
page %>%
  html_elements(".summary_taste p , .summary_milk p , .summary_moisture_and_type p , .summary_family p , .summary_country p") %>%
  html_text(trim = TRUE) %>%
  tibble()
```

```{r}

```


function writing
```{r}
grab_text <- function(page, css){
  
  page %>%
    html_elements(css) %>%
    html_text(trim = TRUE)
}

scrape <- function(link, delay = 1) {
  Sys.sleep(delay)
  
  page <- read_html(link)
  
  
}
```

